Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2019-08-19 resistingrhythm/analysis/paper_figures_v4.Rmd
Fix labels

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

>>>>

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Tonic", nrow(df))
